---
title: "facebook_metrics"
output: pdf_document
---

```{r}
library(tidyverse)
library(MASS)
library(dplyr)
```



```{r}
data = read.csv(file = 'Test_Case_1.csv', header = F)
data
```

```{r}
#data = read.csv(file = 'Features_TestSet.csv', header = F)
#data
```




```{r}
cols = c("Page Popularity", "Page Checkins", "Page talking about", "Page Category",
        "C1_0", "C1_1", "C1_2", "C1_3", "C1_4",
        "C2_0", "C2_1", "C2_2", "C2_3", "C2_4",
        "C3_0", "C3_1", "C3_2", "C3_3", "C3_4",
        "C4_0", "C4_1", "C4_2", "C4_3", "C4_4",
        "C5_0", "C5_1", "C5_2", "C5_3", "C5_4",
        "CC1", "CC2", "CC3", "CC4", "CC5",
        "Base time", "Post length", "Post Share Count", "Post Promotion Status", "H Local",
        "Pub0", "Pub1", "Pub2", "Pub3", "Pub4", "Pub5", "Pub6",
        "Dt0", "Dt1", "Dt2", "Dt3", "Dt4", "Dt5", "Dt6",
        "Target Variable")

colnames(data) = cols
data
```


```{r}
add_later = c("Page Category")

vars = c("Page Popularity", "Page Checkins", "Page talking about",
         "Post length", "Post Share Count","H Local", "Target Variable")

metrics = data[vars]

# Normalize Comments
metrics["Comments/Hr"] = metrics["Target Variable"]/metrics["H Local"]

# Remove H Local and Target Variable
vars = c("Page Popularity", "Page Checkins", "Page talking about", 
         "Post length", "Post Share Count", "Comments/Hr")
metrics = metrics[vars]

# Set null values to 0
metrics[is.na(metrics)] = 0

# Avoid 0 values in response
metrics$`Comments/Hr` = metrics$`Comments/Hr` + 0.00000001

# Avoid 0 values in predictors
metrics$`Page Checkins` = metrics$`Page Checkins` + 0.00000001
metrics$`Post length` = metrics$`Post length` + 0.00000001

# Remove Outliers
summary(metrics$`Post Share Count`)

metrics = metrics %>% arrange(desc(`Post Share Count`)) %>%
        slice(-1:-2)

outlier.test.model = lm(`Comments/Hr` ~ ., data = metrics)
rs = rstandard(outlier.test.model)
rs #7, 39

metrics = metrics %>% arrange(desc(`Post Share Count`)) %>%
        slice(-7,-39)

metrics
```


```{r}
model = lm(`Comments/Hr` ~ ., data = metrics)
summary(model)
```


```{r}
pairs(metrics)
```


## Stepwise Regression

```{r}
# predictors
comments = metrics$`Comments/Hr`
popularity = metrics$`Page Popularity`
checkins = metrics$`Page Checkins`
talkabt = metrics$`Page talking about`
postlen = metrics$`Post length`
sharecount = metrics$`Post Share Count`
```

```{r}
mod0 = lm(comments ~ 1)
add1(mod0, ~.+popularity+checkins+talkabt+postlen+sharecount, test = 'F')
```

```{r}
mod1 = update(mod0, ~.+talkabt)
add1(mod1, ~.+popularity+checkins+postlen+sharecount, test = 'F')
```

```{r}
mod2 = update(mod1, ~.+popularity)

# Check that added variable does not affect original predictors
summary(mod2)
```

```{r}
add1(mod2, ~.+checkins+postlen+sharecount, test = 'F')
```

`mod2` seems to be the best model for our target variable.

```{r}
plot(fitted(mod2), resid(mod2), xlab = 'Fitted Values', ylab = 'Residuals', main = 'Residuals vs Fitted Value')
```

```{r}
boxcox(mod2, lambda = seq(-1, 1, length = 10))
```

```{r}
model = lm(comments^0.2 ~ talkabt + popularity)
plot(fitted(model), resid(model), xlab = 'Fitted Values', ylab = 'Residuals', main = 'Residuals vs Fitted Value')
```
```{r}
summary(model)
```

```{r}
par(mfrow=c(1,2))


plot(fitted(lm(comments^0.2 ~ talkabt)), resid(lm(comments^0.2 ~ talkabt)), xlab = 'Popularity', ylab = 'Residuals', main = 'Residuals vs Page Talkin About')

plot(fitted(lm(comments^0.2 ~ popularity)), resid(lm(comments^0.2 ~ popularity)), xlab = 'Checkins', ylab = 'Residuals', main = 'Residuals vs Page Popularity')
```


```{r}
par(mfrow=c(1,2))

model.t.x1 = lm(comments^0.2 ~ log(talkabt))
model.t.x2 = lm(comments^0.2 ~ log(popularity))

plot(fitted(model.t.x1), resid(model.t.x1), xlab = 'Popularity', ylab = 'Residuals', main = 'Residuals vs Page Talkin About')

plot(fitted(model.t.x2), resid(model.t.x2), xlab = 'Checkins', ylab = 'Residuals', main = 'Residuals vs Page Popularity')
```


```{r}
model.transform = lm(comments^0.2 ~ log(talkabt) + log(popularity))
summary(model.transform)
```

```{r}
plot(fitted(model.transform), resid(model.transform), xlab = 'Fitted Values', ylab = 'Residuals', main = 'Residuals vs Fitted Value')
```

```{r}
qqnorm(resid(model.transform))
qqline(resid(model.transform))
```

```{r}
outlier.test.model = lm(`Comments/Hr` ~ ., data = metrics)
rs = rstandard(outlier.test.model)
rs #7, 39
```


```{r}
summary(metrics)
#find average data
avgdata = data.frame(talkabt = mean(talkabt),
                     popularity = mean(popularity))
predict(model.transform, avgdata, interval = "confidence", level = 0.95) #0.8772555 0.730987 1.023524
prediction = 0.8772555^(1/0.2)
prediction
ci.lower = 0.730987^(1/0.2)
ci.lower
ci.upper = 1.023524^(1/0.2)
ci.upper
```



\newpage


# Research Question 1:  

```{r}
model.transform
```


$Y = 0.2089 + 0.2202x_1 - 0.1359x_2$

$\beta_0 = 0.07223$  
$\beta_1 = 0.18196$  
$\beta_2 = -0.09729$

# Research Question 2:

Can the number of comments received per hour be predicted by at least one of our selected variables?  

$H_0: \beta_1 = \beta_2 = 0$  
$H_1: \text{At least one } \beta_k \neq 0 $ (k = 1,2)  
$\alpha = 0.05$

```{r}
mod.full2 = lm((comments)^0.2 ~ log(talkabt) + log(popularity))
mod.reduced2 = lm((comments)^0.2 ~ 1)
anova(mod.reduced2, mod.full2)
```

F-Statistic = 7.8878  
P-value = 0.0006851

Since p-value is less than alpha, we reject the null hypothesis. There is sufficient evidence to suggest that at least one of the slope parameters is not equal to 0 and one of our selected predictors is useful in predicting comments/hr.  

Research Question 3:  

# Hypothesis test for testing that one slope parameter is 0.

$H_0: \beta_2 = 0$  
$H_1: \beta_2 \neq 0 $
$\alpha = 0.05$


```{r}
mod.reduced = lm((comments)^0.2 ~ log(popularity))
mod.full = lm((comments)^0.2 ~ log(talkabt) + log(popularity))
anova(mod.reduced, mod.full)
```

F-Statistic = 11.579  
P-Value = 0.0009855  

Our p-value is less than 0.05 so we reject the null hypothesis and conclude that page popularity is significantly linearly related to comments/hr.


```{r}
summary(metrics)
```
















































